### 2015-07-19 A2/writeup.tex
Add changes to writeup.tex.

\section{Design}
My program is a state machine which uses getopt to parse through commands. When it reads the "q" option, it puts itself in APPEND mode. This causes it to iterate through
the further arguments to the program and parse them as input files. When it reads the "x" option, it puts itself in EXTRACT mode. This causes it to read the arfile argument
and create files from that archive. Etc etc etc.

@@

@@

\section{Questions}
Point of assignment: To get us used to the level of difficulty of programming assignments, to give an introduction to system programming and file IO. \\
Correctness testing: By running the ar command and checking for exact duplication of behavior. \\
Learn: Start earlier! Also lots about IO and string manipulation.\\

>>>>

\section{Design}
My program is a state machine which uses getopt to parse through commands. When it reads the "q" option, it puts itself in APPEND mode. This causes it to iterate through
the further arguments to the program and parse them as input files. When it reads the "x" option, it puts itself in EXTRACT mode. This causes it to read the arfile argument
and create files from that archive. Etc etc etc. \\

@@

July 17th 3:00pm - 1:00am: Fixed bugs in outputting archive file properly (\n-padding odd outputs). Spent a long time debugging delete option problem. \\

July 18th 4:00pm-8:00pm: Fixed delete option problem. Checked for errors, fixed minor ones. Finished worklog. \\

@@

I also spent a considerable amount of time on the delete code. I was having problems with my pointer references and knowing where I was in the file. I spent an overly long
amount of time trying to fix a bug, then eventually rewrote the entire section of code in about 20 minutes. I should have done that sooner. I think that for me, it is much 
easier to rewrite code that involves strings and pointers than to debug existing code. \\

\section{Questions}
Point of assignment: To get us used to the level of difficulty of programming assignments, to give an introduction to system programming and file IO. To show how complicated
even simple Linux tools are. \\
Correctness testing: By running the ar command and checking for exact duplication of behavior. Also by checking to see if output from myar could be run with ar and 
vice versa. I ran most of my tests with simple 3-character .txt files. The program works with more complicated text files; I can't imagine it working differently for larger
files than 3-character ones. \\
Learn: I learned next time I need to start earlier. Also I learned lots about IO and string manipulation.\\
